Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-11-30 paper_comparison/paper_comparison/paper_comparison.Rmd
update power plots
add plot selection section

>>>>

## Visual test

Note that both the p-value and power comparison are not directly based on the diagnostic plots recommended by abundance of literature, but

## Lineup selection

```{r cache = TRUE}
vi_survey_with_plot <- vi_survey %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  left_join(map_df(1:length(vi_lineup), 
    ~vi_lineup[[.x]]$data %>% 
      group_by(k) %>% 
      summarise(plot_p_value = first(p_value)) %>%
      arrange(k) %>%
      mutate(unique_lineup_id = names(vi_lineup)[.x]) %>%
      mutate(plot_p_value_rank = rank(plot_p_value, ties.method = "min"))) %>%
  pivot_wider(values_from = c(plot_p_value, plot_p_value_rank), names_from = k, names_prefix = "plot_")) %>%
  (function(x) {
      for (i in 1:20)
        x[[paste0("plot_sel_plot_", i)]] <-
          grepl(paste0("_", i, "_"), x$selection) |
          grepl(paste0("^", i, "_"), x$selection) |
          grepl(paste0("_", i, "$"), x$selection) |
          grepl(paste0("^", i, "$"), x$selection)
      x}
    ) %>%
  pivot_longer(plot_p_value_plot_1:plot_sel_plot_20, 
               names_to = c(".value", "plot"), 
               names_pattern = "(.*)_plot_(.+)") 
```

```{r dataplotsel, fig.cap = "..."}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            weighted_detect = sum(weighted_detect),
            n_eval = n()) %>%
  group_by(plot_p_value_rank) %>%
  summarise(weighted_detect = sum(weighted_detect),
            n_eval = sum(n_eval)) %>%
  ggplot() +
  geom_col(aes(factor(plot_p_value_rank), n_eval)) +
  geom_col(aes(factor(plot_p_value_rank), weighted_detect, fill = "weighted number of detections")) +
  xlab("Data plot p-value rank") +
  ylab("Number of Lineups") +
  theme(legend.position = "bottom") +
  labs(fill = "")
```

```{r dadtaplotselfacet, fig.cap = "..."}
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  left_join(vi_survey_with_plot %>%
              filter(!attention_check) %>%
              filter(!null_lineup) %>%
              filter(answer == plot) %>%
              group_by(unique_lineup_id) %>%
              summarise(answer_rank = first(plot_p_value_rank))) %>%
  mutate(weighted_sel = ifelse(num_selection == 0, 0.05, plot_sel/num_selection)) %>%
  group_by(plot_p_value_rank, answer_rank) %>%
  summarise(weighted_sel = sum(weighted_sel)) %>%
  ggplot() +
  geom_col(aes(factor(plot_p_value_rank), weighted_sel)) +
  geom_vline(data = data.frame(answer_rank = 1:20, x = 1:20),
             aes(xintercept = x),
             col = "red") +
  facet_wrap(~answer_rank, scales = "free_y") +
  xlab("Plot p-value rank") +
  ylab("Weighted number of selections")
```

```{r eval = FALSE}
# data plot not always has the lowest conventional p-value
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  ggplot() +
  geom_bar(aes(factor(plot_p_value_rank)))

# according to the rank of the data plot p-value, how many people select it 
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(plot_sel) %>%
  left_join(vi_survey_with_plot %>%
              filter(!attention_check) %>%
              filter(!null_lineup) %>%
              filter(answer == plot) %>%
              group_by(unique_lineup_id) %>%
              summarise(answer_rank = first(plot_p_value_rank))) %>%
  ggplot() +
  geom_bar(aes(factor(plot_p_value_rank))) +
  geom_vline(data = data.frame(answer_rank = 1:20, x = 1:20),
             aes(xintercept = x),
             col = "red") +
  facet_wrap(~answer_rank, scales = "free_y")

# For different rank, percentage of subject select it
vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id, set) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            detect = first(detect),
            type = first(type)) %>%
  ggplot() +
  geom_bar(aes(factor(plot_p_value_rank), fill = detect), position = "fill") +
  geom_hline(yintercept = 0.05) +
  xlab("Data plot p-value rank") +
  ylab("Propotion of subject detecting the data plot")

vi_survey_with_plot %>%
  filter(!attention_check) %>%
  filter(!null_lineup) %>%
  filter(answer == plot) %>%
  group_by(unique_lineup_id, set) %>%
  summarise(plot_p_value_rank = first(plot_p_value_rank),
            prop_detect = first(prop_detect)) %>%
  ggplot() +
  geom_boxplot(aes(factor(plot_p_value_rank), prop_detect))

# vi_survey_with_plot %>%
#   filter(!attention_check) %>%
#   filter(!null_lineup) %>%
#   filter(answer == plot) %>%
#   group_by(unique_lineup_id, set) %>%
#   summarise(plot_p_value_rank = first(plot_p_value_rank),
#             conv_detect = first(conventional_p_value < 0.05)) %>%
#   ggplot() +
#   geom_bar(aes(factor(plot_p_value_rank), fill = conv_detect), position = "fill") +
#   xlab("Data plot p-value rank") +
#   ylab("Propotion of subject detecting the data plot")
```

\pagebreak

### 2022-11-30 paper_comparison/paper_comparison/paper_comparison.tex
update power plots
add plot selection section

>>>>

\hypertarget{visual-test}{%
\subsection{Visual test}\label{visual-test}}

Note that both the p-value and power comparison are not directly based
on the diagnostic plots recommended by abundance of literature, but

\hypertarget{lineup-selection}{%
\subsection{Lineup selection}\label{lineup-selection}}

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/dataplotsel-1}

\caption{...}\label{fig:dataplotsel}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/dadtaplotselfacet-1}

\caption{...}\label{fig:dadtaplotselfacet}
\end{figure}

\pagebreak
